### 2020-06-02 report/sections/general/p2p.tex
Report: minor style change to chapter 7

For example, consider the global type
\[
A \to B: \tmsg{M1}. S \to B: \tmsg{M2}. \texttt{end}
\]
By existing LTS semantics over
global types (\cref{subsubsection:lts}), the sequence 
$[SB!\tmsg{M2}, AB!\tmsg{M1}]$
is a prefix of a valid execution trace.
If we define our routing construct simply by replacing every single
$A \to B: \tmsg{M}$ interaction with $A \to S: \tmsg{M}.
S \to B: \tmsg{M}$, we transform the global type into
\[
A \to S: \tmsg{M1}. S \to B: \tmsg{M1}. S \to B: \tmsg{M2}. \texttt{end}
\]
our naive definition of routing has over-serialised the protocol
since $SB!\tmsg{M2}$ can no longer occur before $AB!\tmsg{M1}$.
This implies that we need to handle routing interactions differently
from ``normal'' send/receive actions.

>>>>

\begin{example}[Naive definition of routing in global types]
Consider the global type
\[
A \to B: \tmsg{M1}. S \to B: \tmsg{M2}. \texttt{end}
\]
By existing LTS semantics over
global types (\cref{subsubsection:lts}), then $SB!\tmsg{M2}$
is a prefix of a valid execution trace.
If we define our routing construct simply by replacing every single
$A \to B: \tmsg{M}$ interaction with $A \to S: \tmsg{M}.
S \to B: \tmsg{M}$, we transform the global type into
\[
A \to S: \tmsg{M1}. S \to B: \tmsg{M1}. S \to B: \tmsg{M2}. \texttt{end}
\]
our naive definition of routing has over-serialised the protocol
since $SB!\tmsg{M2}$ can no longer occur first because \trole{S}
is forced to send \tmsg{M1} first, which it cannot do so until receiving
from \trole{A}.
This implies that we need to handle routing interactions differently
from ``normal'' send/receive actions.
\end{example}
